---
title: "OSMGeosample"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OSMGeosample - An R package for Geostatistical Sampling Designs with OSM Data.}
  %\VignetteEngine{knitr::knitr}
  %\VignetteKeyword{geosample}
  %\VignetteKeyword{package}
  %\VignetteKeyword{vignette}
  %\VignetteKeyword{LaTeX}
  %\VignettePackage{geosample}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  # collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(osmgeosample)
```
\author{Michael G Chipeta\\University of Oxford\And
        Barry Rowlingson\\Lancaster University \And
				Peter J Diggle\\Lancaster University}
\title{\pkg{geosample}: an \proglang{R} Package for Geostatistical Sampling Designs}

\Plainauthor{Michael G Chipeta, Barry Rowlingson, Peter J Diggle} %% comma-separated
\Plaintitle{geosample: an R Package for Geostatistical Sampling Designs} %% without formatting
\Shorttitle{\pkg{geosample}: an \proglang{R} Package for Geostatistical Sampling Designs} %% a short title (if necessary)

\Abstract{We introduce a new \proglang{R} package, \pkg{OSMGeosample}, for constructing geostatistical sampling designs with OSM data. The new package implements classes of \textit{adaptive} and \textit{non-adaptive} probability-based sampling designs. We illustrate the use of the package through the construction of several sampling designs, using a boundary dataset and OSM building data for a slum in Idikan.}

\Keywords{inhibitory sampling designs, geostatistics, \proglang{R}}
\Plainkeywords{inhibitory sampling designs, geostatistics, R} %% without formatting

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Michael G Chipeta, Big Data Institute, University of Oxford, Oxford, OX3 7LF, UK\\
  E-mail: \email{mchipeta@mlw.mw}%\\
  %URL: \url{http://www.lancs.ac.uk}\\[1em]
  %Peter J Diggle\\
  %E-mail: \email{p.diggle@lancaster.ac.uk}\\
  %URL: \url{http://www.lancaster.ac.uk/staff/diggle/}\\[1em]
  }
