---
title: "OSMGeosample"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OSMGeosample - An R package for Geostatistical Sampling Designs with OSM Data.}
  %\VignetteEngine{knitr::knitr}
  %\VignetteKeyword{geosample}
  %\VignetteKeyword{package}
  %\VignetteKeyword{vignette}
  %\VignetteKeyword{LaTeX}
  %\VignettePackage{geosample}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  # collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(osmgeosample)
```
\author{Michael G Chipeta\\University of Oxford\And
        Barry Rowlingson\\Lancaster University \And
				Peter J Diggle\\Lancaster University}
\title{\pkg{geosample}: an \proglang{R} Package for Geostatistical Sampling Designs}

\Plainauthor{Michael G Chipeta, Barry Rowlingson, Peter J Diggle} %% comma-separated
\Plaintitle{geosample: an R Package for Geostatistical Sampling Designs} %% without formatting
\Shorttitle{\pkg{geosample}: an \proglang{R} Package for Geostatistical Sampling Designs} %% a short title (if necessary)

\Abstract{We introduce a new \proglang{R} package, \pkg{OSMGeosample}, for constructing geostatistical sampling designs with OSM data. The new package implements classes of \textit{adaptive} and \textit{non-adaptive} probability-based sampling designs. We illustrate the use of the package through the construction of several sampling designs, using a boundary dataset and OSM building data for a slum in Idikan.}

\Keywords{inhibitory sampling designs, geostatistics, \proglang{R}}
\Plainkeywords{inhibitory sampling designs, geostatistics, R} %% without formatting

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Michael G Chipeta, Big Data Institute, University of Oxford, Oxford, OX3 7LF, UK\\
  E-mail: \email{mchipeta@mlw.mw}%\\
  %URL: \url{http://www.lancs.ac.uk}\\[1em]
  %Peter J Diggle\\
  %E-mail: \email{p.diggle@lancaster.ac.uk}\\
  %URL: \url{http://www.lancaster.ac.uk/staff/diggle/}\\[1em]
  }
  
  
  
---------------
## Introduction
---------------

* Bulleted list
* Item 2
    * Nested bullets need a 4-space indent.
    * Item 2b
    
    
1.  Item 1.
    *  Item a
    *  Item b
1.  Item 2.
    
Definition
  : a statement of the exact meaning of a word, especially in a dictionary.
List 
  : a number of connected items or names written or printed consecutively, 
    typically one below the other. 
  : barriers enclosing an area for a jousting tournament.

_italic_ or *italic*
__bold__ or **bold**    
[link text](destination)
<http://this-is-a-raw-url.com>


| Right | Left | Default | Center |
|------:|:-----|---------|:------:|
|   12  |  12  |    12   |    12  |
|  123  |  123 |   123   |   123  |
|    1  |    1 |     1   |     1  |


```
# A comment
add <- function(a, b) a + b
```


```c
int add(int a, int b) {
  return a + b;
}
```

```{r}
# Add two numbers together
add <- function(a, b) a + b
add(10, 20)
```


```r
# Add two numbers together
add <- function(a, b) a + b
add(10, 20)
## [1] 30
```

# Add two numbers together
add <- function(a, b) a + b
add(10, 20)
## 30.




--------------------------------------------------------
 Sepal.Length   Sepal.Width   Petal.Length   Petal.Width 
-------------- ------------- -------------- -------------
     5.1            3.5           1.4            0.2     

     4.9             3            1.4            0.2     

     4.7            3.2           1.3            0.2     
---------------------------------------------------------




osmdata is an R package for downloading and using data from OpenStreetMap (OSM). OSM is a global open access mapping project, which is free and open under the ODbL licence (OpenStreetMap contributors 2017). This has many benefits, ensuring transparent data provenance and ownership, enabling real-time evolution of the database and, by allowing anyone to contribute, encouraging democratic decision making and citizen science (Johnson 2017). See the OSM wiki to find out how to contribute to the world’s open geographical data commons.

Unlike the OpenStreetMap package, which facilitates the download of raster tiles, osmdata provides access to the vector data underlying OSM.

osmdata can be installed from CRAN with
